\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
%\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
%\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent

\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 bottom=20mm,
 }

\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{enumerate}
\usepackage{arcs}
\usepackage{subfiles}
\usepackage{enumitem}
\usepackage{pifont}
\usepackage{multirow}
\usepackage{ctex}

%SetFonts

%SetFonts

\usepackage[inline]{asymptote}



\pagestyle{fancy}
\fancyhf{}
\rhead{Teacher's contact: anna.yan8641@gmail.com}
\lhead{\leftmark}
\lfoot{Copyright \copyright  2019 - 2023 by Teacher Anna. All rights reserved.}
\rfoot{Page \thepage}

\title{父亲}
\author{钟子飞}
\date{June 7, 2023}							% Activate to display a given date or no date
\begin{document}

\newlist{choices}{enumerate}{1}
\setlist[choices]{label*=(\Alph*)}
\setlistdepth{1} 

\maketitle


\section{最后的日子}
2016年10月26日，周六早晨8点左右，我接到舅舅电话，说父亲昨晚睡下直到现在还没醒来。

“叫不醒他了。”舅舅在电话里面说到。

听到消息，我一下子从床上弹起来，一边穿衣一边告诉爱人严菲：“我爸或许要走了。他醒不来了。”我言语中带着一丝哭腔。

我立即买好机票，奔向重庆老家。飞机降落重庆机场，已经中午12点。舅舅再来电话，说父亲已经离开了。

我的父亲永远离开了我。




\end{document}  


